\section{User Interviews}

We conducted some interviews to have a deeper and less biased understanding of
what people need when it comes to ordering takeaway food. The following
points came out:

\begin{itemize}
    \item Many people order takeaway food, at least sometimes. Most of them think
    that it is convenient since they do not have to cook. It also is a way to
    eat some particular food, that can be different from the usual.
    \item Some people are used to call restaurants to make orders, while others
    leverage food ordering apps. Somebody goes to restaurants in person to place
    an order.
    \item People that use apps think that it is a great way to order food without
    risking that the information comes across as incorrect, as it could happen
    with a phone call. Apps make it easier to check the menu, check the status
    of an order, and discover new restaurants. However, apps sometimes contain
    bugs. Somebody complains about having to call a restaurant multiple
    times because the line is busy. A waiter could be useful to give advice.
    \item Some people would feel comfortable ordering food with a voice chatbot.
    They think that it is fast and easy to interact via voice and it would feel
    similar to talking to a human, but in a more accurate way. Additionally, some
    claim to be technology enthusiasts and would appreciate such a situation.
    Others, instead,
    think that they would not feel comfortable talking to a bot.

\end{itemize}

All interviews conducted are available in the +++++ section.
