\section{Wizard of Oz Test}

Before starting to develop our voice chatbot, we applied a prototyping technique to
test the main use cases on real users. These tests allowed us to detect
various weak points in the interaction between the two actors and change the
voice interface accordingly. The chosen technique is the Wizard of Oz. It consists
of a person that pretends to be the voice chatbot and formulates sentences according
to the pre-defined rules. The user, on the other hand, does not know that he is interacting
with a human but thinks that there is a machine on the other side. We applied this
technique both through text messages and through voice.

\subsection{Text Messages Test}

\subsubsection*{ \underline{Test n°1:} }

\begin{itemize}

\item[\textbf{Bot:}] Welcome to HeyFood.
What pizza would you like to order? For example, you can ask me for a pepperoni pizza with extra cheese, and I will suggest you the most similar pizza available on the menu.

\item[\textbf{User:}] I would like a Margherita

\item[\textbf{Bot:}] Ok, we have the Margherita pizza. Its ingredients are: tomato, mozzarella cheese. It costs 10 euros. Is that fine?

\item[\textbf{User:}] With extra cheese

\item[\textbf{Bot:}] I am sorry, I didn’t quite get it. What pizza would you like to order? For example you can ask me for a pepperoni pizza with extra cheese, and I will suggest you the most similar pizza available on the menu.

\item[\textbf{User:}] I would like a margherita pizza with extra cheese

\item[\textbf{Bot:}] Ok, we have the Margherita pizza. Its ingredients are: tomato, mozzarella cheese. It costs 10 euros. Is that fine?

\item[\textbf{User:}] Yes

\item[\textbf{Bot:}] How many Margherita pizzas would you like to order?

\item[\textbf{User:}] 1

\item[\textbf{Bot:}] Okay, it’s 10 euros so far. Would you like to add anything else?

\item[\textbf{User:}] Yes please

\item[\textbf{Bot:}] What pizza would you like to order?

\item[\textbf{User:}] A veggie

\item[\textbf{Bot:}] Ok, we have the Special Veggie. Its ingredients are: green peppers, onions, tomatoes, mushrooms, black olives and cheese. It costs 15 euros. Is that fine?

\item[\textbf{User:}] Yes

\item[\textbf{Bot:}]How many Special Veggie pizzas would you like to order?

\item[\textbf{User:}] 2

\item[\textbf{Bot:}] Okay, it’s 25 euros so far. Would you like to add anything else?

\item[\textbf{User:}] No thanks

\item[\textbf{Bot:}] Perfect, your order is 25 euros. You ordered one Margherita and two Special Veggie. Is the order correct? Otherwise you can start over saying-> no.

\item[\textbf{User:}] Yes

\item[\textbf{Bot:}] Okay, your order is confirmed at 20:15 and the order number is 42. Please communicate it at your arrival. Thanks for choosing us, and buon appetito!


\end{itemize}

%\newpage

\vspace{0.5cm}
\subsubsection*{\underline{Test n°2:} }

\begin{itemize}

\item[\textbf{Bot:}] Welcome to HeyFood.
What pizza would you like to order? For example, you can ask me for a pepperoni pizza with extra cheese, and I will suggest you the most similar pizza available on the menu.


\item[\textbf{User:}] I would like to order a capricciosa pizza

\item[\textbf{Bot:}] Ok, we have the Capricciosa pizza. Its ingredients are: ham, egg, tomato, mushrooms, mozzarella cheese. Is that fine?

\item[\textbf{User:}] Yes

\item[\textbf{Bot:}]How many Capricciosa pizzas would you like to order?

\item[\textbf{User:}] 2

\item[\textbf{Bot:}] Okay, it’s 8 euros so far. Would you like to add anything else?

\item[\textbf{User:}]no thank you

\item[\textbf{Bot:}] Perfect, your order is 8 euros. You ordered  two Capricciosa pizzas. Is the order correct? Otherwise you can start over saying no.


\item[\textbf{User:}] It is correct

\item[\textbf{Bot:}] Ok

\end{itemize}


\newpage

\subsection{Voice Test}

\subsubsection*{\underline{Test n°3:} }

\begin{itemize}

\item[\textbf{Bot:}] Welcome to HeyFood.
What pizza would you like to order? For example, you can ask me for a pepperoni pizza with extra cheese, and I will suggest you the most similar pizza available on the menu.


\item[\textbf{User:}] A Margherita

\item[\textbf{Bot:}] Ok, we have the Margherita pizza. Its ingredients are: tomato, mozzarella cheese. Is that fine?

\item[\textbf{User:}]Yes

\item[\textbf{Bot:}] How many Capricciosa pizzas would you like to order?

\item[\textbf{User:}]2

\item[\textbf{Bot:}]Okay, it’s 7 euros so far. Would you like to add anything else?

\item[\textbf{User:}]No

\item[\textbf{Bot:}] Perfect, your order is 7 euros. You ordered  two Margherita pizzas. Is the order correct? Otherwise you can start over saying no.

\item[\textbf{User:}]Yes

\item[\textbf{Bot:}]Ok

\end{itemize}

