\section{Real Ordering Calls}

In this section, we report two real examples of phone calls to the restaurant made by
customers that want to order their food. This is extremely important because we want
to understand the practical flow of the conversation and the various problems that
could arise in the real-world scenario.

\subsection*{First Call}

\begin{itemize}

\item[\textbf{Restaurant:}] Good Evening, \textit{**********} Restaurant.

\item[\textbf{Customer:}] Hi, I'd like to order some pizzas for tonight, is it possible? 

\item[\textbf{Restaurant:}] Sure sir, absolutely, will you come here or will we bring them to you? 

\item[\textbf{Customer:}] I want takeaway.

\item[\textbf{Restaurant:}] At what time did he want? 

\item[\textbf{Customer:}]  8:30

\item[\textbf{Restaurant:}] 8:30 sir it is not possible we are already full, it is ok 8:15 or 8:45? 

\item[\textbf{Customer:}] 8:15 is ok. 

\item[\textbf{Restaurant:}] Perfect, leave me a name. 

\item[\textbf{Customer:}] Moretti

\item[\textbf{Restaurant:}] Yes, please list me the pizzas.

\item[\textbf{Customer:}]  One margherita

\item[\textbf{Restaurant:}] yes..

\item[\textbf{Customer:}]   then two friarielli and salsiccia.

\item[\textbf{Restaurant:}] Something else, sir?

\item[\textbf{Customer:}]   No thanks, that's ok.

\item[\textbf{Restaurant:}] Okay, kindly leave me a phone number.

\item[\textbf{Customer:}]   328 *** **** .

\item[\textbf{Restaurant:}] Perfect, see you this evening, have a nice day!.

\end{itemize}

\newpage

\subsection*{Second Call}

\begin{itemize}

\item[\textbf{Restaurant:}] Good Evening, \textit{**********} Restaurant.

\item[\textbf{Customer:}] Hi, I want some pizzas for tonight at home.

\item[\textbf{Restaurant:}] Yes, at what time? 

\item[\textbf{Customer:}]  8:15

\item[\textbf{Restaurant:}] 8:15 sir it is not possible, is it ok for 7:45? 

\item[\textbf{Customer:}] 7:45 is fine. 

\item[\textbf{Restaurant:}] Perfect, leave me the surname on the intercom. 

\item[\textbf{Customer:}] Cingolani

\item[\textbf{Restaurant:}] Yes, please list me the pizzas. 

\item[\textbf{Customer:}]  One Bufala and Porcini

\item[\textbf{Restaurant:}] yes.. then?

\item[\textbf{Customer:}]   One with the anchovies 

\item[\textbf{Restaurant:}] Do you mean a Napoli?

\item[\textbf{Customer:}]   Yes, exactly.

\item[\textbf{Restaurant:}] Do you want something else, a suppli, a bottle of coca cola?

\item[\textbf{Customer:}]   Why not, also two suppli, thanks.

\item[\textbf{Restaurant:}] Okay, please give me your home address. 

\item[\textbf{Customer:}]   Via di San Martino 2**

\item[\textbf{Restaurant:}] Okay, kindly leave me also a phone number.

\item[\textbf{Customer:}]   380 *** **** .

\item[\textbf{Restaurant:}] Perfect, the total price is 16€, you have to pay to the delivery-man.

\item[\textbf{Customer:}]   Thanks a lot, I'll wait for you tonight.

\end{itemize}
