\section{Similar services analysis}

We analyzed several similar services. So, we looked into some food-ordering
voice chatbots available online. These are a few of those.

\subsection{RunnerPizza's Skill}

It's a service that lets customers order pizza via a chatbot (Alexa).
It's possible to make a new order, select a specific pizza from the
list of pizzas available and finally choose delivery time and the address.
Alexa provides feedback to the customer after each completed step in the process.
The interaction is very intuitive and simple due to the developed schematic process,
and in this way, every type of user is able to make a new order. The whole process
takes very few minutes. On the other hand, it's only possible to check/modify or delete
the order on RunnerPizza's website and this is the big limitation of this service.
The power of this type of service is given by the use of the voice, which in the
meantime allows the customer to do other things. So, each task related to this kind
of service should also be completed with the voice.
Even if our service takes into account different types of food and implements
other operations related to the order (e.g. checking the status of the
order via Alexa),
this service is a very good starting point for what we want to achieve.

\subsection{Domino's Skill}

This skill is provided by Domino's Pizza; it allows the user to place pizza orders 
in their restaurants. Differently from RunnerPizza, this skill also lets you check
the status of an order. Also in this case, the limitation is given by the fact that
the system only works for one franchise of restaurants.


\subsection{Starbucks Reorder's Skill}

Pretty simple, it basically only allows you to place (usual) orders that were originally
done through the app. Free to use, limited to a few functions, and also allows you
to check the balance of the associated card. The app provides you with a history of your
orders so that you can place an old order again. After that, it gives you a list of
physical coffee shops where you can collect your order.